---
title: "Jijou's App documentation"
author: "Joanne Breitfelder"
date: "29 Jul 2016"
output: html_document
---

*****
## Introduction

Jijou's app allows you to find interesting places around you.  
Looking for a good pizzeria, an aquarium, or the closest dentist? This app is for you! :) 
  
```{r, out.width=200, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
include_graphics("logos.pdf")
```  

This application is based on [RStudio's Shiny](http://shiny.rstudio.com) and [Google Maps API](https://developers.google.com/maps/).

#### Links

To access the app: <https://jijou.shinyapps.io/Jijou-s-app/>  
Github repository: <https://github.com/jbreitfelder/Jijou-s-app>

#### How to use this app?

1. Enter the kind of place you are looking for.
2. Enter your location
3. Choose the radius in which you want to look for (only the 20 closest results will be desplayed)
4. Adjust the map zoom: from 3 (continent) to 21 (building).
5. Actualize and enjoy :)  

#### Our users around the world speak about us!

* *En tant qu'utilisateurs on est conquis!*
Mélanie, **France**

* *On aime beaucoup le design, le retour à la simplicité!*
Damien, **France**

* *Súper chévere y facil de usar! Aunque no encontré la pizzeria al lado de mi casa..* 
Juan, **Brazil**  


*****
## How does it work?

#### Geocoding with Google Maps API

The application is based on 2 functions using Google Maps API. The first one, `geoCode()`, allows to find the GPS coordinates of a given place, and I found it [here](https://gist.github.com/josecarlosgonz/6417633). Let's see an example of what it does :

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(shiny)
library(RCurl)
library(jsonlite)
library(plyr)
library(ggmap)
library(curl)

url <- function(address, return.call="json", sensor="false") {
        root <- "http://maps.google.com/maps/api/geocode/"
        u <- paste(root, return.call, "?address=", 
                   address, "&sensor=", sensor, sep="")
        return(URLencode(u))
}

geoCode <- function(address) {
        u <- url(address)
        doc <- getURL(u)
        x <- fromJSON(doc, simplifyVector=FALSE)
        if(x$status=="OK") {
                lat <- x$results[[1]]$geometry$location$lat
                lng <- x$results[[1]]$geometry$location$lng
                location_type <- x$results[[1]]$geometry$location_type
                formatted_address <- x$results[[1]]$formatted_address
                return(c(lat, lng, location_type, formatted_address))
        } else {
                return(c(NA, NA, NA, NA))
        }
}
```

```{r}
geoCode("Johns Hopkins University")
```

#### Finding places of interest with Google Maps API

The second function, `close_places()` returns the 20 closest places of interest around a given position. Here is an example of the general structure of the function:

```{r, eval=FALSE}
close_places <- function(location, radius, place){ 
        
        ## Coordinates of the location
        coord <- geoCode(location)
        coord <- paste(as.character(round(as.numeric(coord[1]), 5)), 
                       as.character(round(as.numeric(coord[2]), 5)), sep=",")
        
        ## Creation of the URL
        baseurl<-"https://maps.googleapis.com/maps/api/place/nearbysearch/json?"
        google_key <- "YOUR-PERSONNAL-KEY"
        newurl <- paste(baseurl,"location=", coord, "&radius=", radius,
                        "&name=", place, "&key=", google_key, sep="")
        
        ## Results
        final <- fromJSON(newurl, simplifyVector=TRUE)
        final <- final$results

        details <- data.frame(icon=final$icon, rating=final$rating,
                              address=final$vicinity,
                              open_now=final$opening_hours$open_now, 
                              name=final$name,
                              idx=1:length(final$geometry$location$lat),
                              lat=final$geometry$location$lat,
                              long=final$geometry$location$lng)
        
        return(details)
}
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
close_places <- function(location, radius, place){ 
        
        ## Coordinates of the location
        coord <- geoCode(location)
        coord <- paste(as.character(round(as.numeric(coord[1]), 5)), 
                       as.character(round(as.numeric(coord[2]), 5)), sep=",")
        
        ## Creation of the URL
        baseurl<-"https://maps.googleapis.com/maps/api/place/nearbysearch/json?"
        google_key <- "AIzaSyD-8mknrSyCYh0Feg5PgGmq8gFIh3GINJo"
        newurl <- paste(baseurl,"location=", coord,
                        "&radius=", radius,
                        "&name=", place,
                        "&key=", google_key, sep="")
        
        ## Results
        final <- fromJSON(newurl, simplifyVector=TRUE)
        final <- final$results
        
        if("opening_hours" %in% names(final)){
                if("open_now" %in% names(final$opening_hours)){
                        open_now <- ifelse(is.na(final$opening_hours$open_now), "No information",
                                         ifelse(final$opening_hours$open_now==FALSE,
                                                "Closed :(", "Open :)"))
                }
        } else {
                open_now <- rep("No information", length(final$name))
        }
        
        rating <- ifelse(is.na(final$rating), mean(final$rating, na.rm=TRUE),
                         final$rating)
        
        icon <- paste("<img src='", final$icon, "' width='50'></img>", sep="")
        
        details <- data.frame(icon=icon,
                              rating=rating,
                              address=final$vicinity,
                              open_now=open_now,
                              name=final$name,
                              idx=1:length(final$geometry$location$lat),
                              lat=final$geometry$location$lat,
                              long=final$geometry$location$lng)
        
        return(details)
}
```

This code has been simplified for clarity, but the complete version is available on my [GitHub repository](https://github.com/jbreitfelder/Jijou-s-app). Let's see an example of how it works :

```{r}
results <- close_places("Johns Hopkins University", 1000, "school")
kable(head(results, 5))
```

#### Visualisation

We can now visualise the result with the `ggmap` library : 

```{r, message=FALSE, warning=FALSE}

coord <- data.frame(lon=as.numeric(geoCode("Johns Hopkins University")[2]),
           lat=as.numeric(geoCode("Johns Hopkins University")[1]))

ggmap(get_map(c(coord$lon, coord$lat), zoom=14)) +
        geom_point(data=results, aes(x=as.numeric(long), 
                                  y=as.numeric(lat)), size=3, alpha=0.8) +
        geom_point(data=coord, aes(x=lon, y=lat), color="orange", size=2) +
        xlab("Longitude") + ylab("Latitude")
```

Let's add some options to make it look a bit more fancy! :)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
make_circles <- function(center=c(0, 0), radius=1, npoints=100){
        meanLat <- center[2]
        radiusLon <- radius/(40075000/360)/cos(meanLat/57.3) 
        radiusLat <- radius/(40075000/360)
        circleDF <- data.frame(ID=1:npoints)
        angle <- seq(0, 2*pi, length.out=npoints)
        
        circleDF$lon <- center[1]+radiusLon*2*cos(angle)
        circleDF$lat <- center[2]+radiusLat*2*sin(angle)
        return(circleDF)
}

circle_data <- make_circles(c(coord$lon, coord$lat), 1000, npoints=100)

                ggmap(get_map(c(coord$lon, coord$lat), zoom=14)) +
                        geom_point(data=results, 
                                   aes(x=as.numeric(long), 
                                       y=as.numeric(lat),
                                       size=rating),
                                   color="black", stroke=0.5) +
                        scale_size("Rating") +
                        geom_point(data=results, 
                                   aes(x=as.numeric(long), 
                                       y=as.numeric(lat),
                                       size=rating,
                                       color=open_now), stroke=0.02) +
                        scale_color_discrete("Can I go now?") +
                        geom_polygon(data=circle_data, aes(x=lon, y=lat), 
                                     fill="SteelBlue", alpha=0.15) +
                        geom_text(data=results, 
                                  aes(x=as.numeric(long), 
                                      y=as.numeric(lat),
                                      label=idx),
                                  check_overlap=TRUE, size=5, vjust=-1.1) +
                        xlab("Longitude") + ylab("Latitude") +
                        guides(colour=guide_legend(override.aes=list(size=5)))
```


*****
## General structure of the shiny application

The scripts are only in a simplified version here. The entire codes can be found in my [GitHub repository](https://github.com/jbreitfelder/Jijou-s-app)


#### ui.R 

```{r, eval=FALSE}
library(shiny)
library(markdown)

shinyUI(navbarPage("Welcome to Jijou's app! :)",
                   
        tabPanel("Map",
                 fluidRow(
                        column(3, wellPanel(
                               h3("Choose your options:"),
                               p("..."))),
                        
                        column(6, 
                               h3("Result of your request:", align="center"),
                               plotOutput("map")),

                        column(3, wellPanel(
                                h3("Why should you use this app?"),
                                p("..."))))),
        
        tabPanel("Table",
                 fluidRow(
                         column(9, 
                                h3("Result of your request:"),
                                dataTableOutput("table")),
                         
                         column(3, wellPanel(
                                 h3("Why should you use this app?"),
                                 p("..."))))),
        
        tabPanel("Documentation",
                 includeHTML("documentation.html"))
))

```


#### server.R 

```{r, eval=FALSE}
library(shiny)
library(ggmap)

geoCode <- function(address){....}
close_places <- function(location, radius, place){....}

shinyServer(function(input, output) {
        output$map <- renderPlot({
                data <- close_places(input$location, 
                                     input$radius, 
                                     input$place)
                
                coord <- data.frame(lon=as.numeric(geoCode(input$location)[2]),
                           lat=as.numeric(geoCode(input$location)[1]))

                ggmap(get_map(c(coord$lon, coord$lat), zoom=input$zoom)) +
                        geom_point(data=results, aes(x=as.numeric(long), 
                                                     y=as.numeric(lat)),
                                   size=3, alpha=0.8) +
                        geom_point(data=coord, aes(x=lon, y=lat),
                                   color="orange", size=2) +
                        xlab("Longitude") +
                        ylab("Latitude")
        })
        
        output$table <- renderDataTable(close_places(input$location, 
                                                     input$radius, 
                                                     input$place)[, c(1, 6, 5, 3, 2, 4)], escape=FALSE)
})
```


******
## References

D. Kahle and H. Wickham. *ggmap: Spatial Visualization with ggplot2*.  
The R Journal, 5(1), **144-161**.  
<http://journal.r-project.org/archive/2013-1/kahle-wickham.pdf>
